---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

> For commercial use contact with me: nik.krichko@gmail.com

# perf.jmeter.reporter
Package provide simple process analyze jemter perforamance results

<!-- badges: start -->
<!-- badges: end -->

The goal of perf.jmeter.reporter is to ...

## Installation

You can install the released version of perf.jmeter.reporter from [CRAN](https://CRAN.R-project.org) with:

``` r
###install.packages("perf.jmeter.reporter")
maybe in future but now only dev version from github




```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nikkrichko/perf.jmeter.reporter")

#install.packages("remotes")
remotes::install_github("nikkrichko/perf.jmeter.reporter")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(perf.jmeter.reporter)
## basic example code
## add in future
```

